An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-05 docs/icccn2009/paper.tex
Fixing my name and some reviews to the first sections of the paper.
git-svn-id: svn://localhost/netbeams/trunk@347 559edde2-a4d4-44e0-96fc-4035e40d7396

\author{\authorblockN{A. Puder, T. Johnson, K. Sales, M. Sales}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: \{arno$\mid$tlj$\mid$klebers$\mid$msales\}@sfsu.edu}
\and
\authorblockN{D. Robinson}
\authorblockA{San Francisco State University \\
Romberg Tiburon Center \\
3150 Paradise Drive \\
Tiburon, CA 94920 \\
EMail: dhr@sfsu.edu}}

@@

Environmental monitoring depends on the reliable collection of
measurements from remotely deployed sensors and the rapid transfer of
those measurements to data centers where processing and analysis may
take place. Typically, sensors are deployed in out-of-the-way
locations where physical access is limited and connections for
telemetry are poor or nonexistent.   Maintaining the data stream from
these sensors places demands on human resources, requiring site visits
to service the sensors and to download data stored on internal memory.
Consequently, there is a lag of days to months between the time the
sensors perform the measurements and the time the measurements becomes
available.   Advances in battery life and anti-fouling technology have
extended service cycles for field sensors, with the unwanted result of
further delaying access to monitoring data.  In addition, the
dependence on field site visits to alter of sensor characteristics,
such as sampling rate, prevents adjustment in monitoring strategy in
response to rapidly developing events (e.g. oil spills, harmful algal
blooms).

To address these problems of data collection from remote
sensors, we propose to develop an automated end-to-end system based on
proven technology that provides a means to program and interrogate
sensors at the remote field locations and to transmit collected
measurements over long distances to data collections centers where the
data is rapidly processed, archived, and made available to potential
users in near real-time.

@@

Researchers in the geosciences rely on sensor data collected by highly
specialized sensors such as the Seabird or YSI. These sensors are
usually deployed in remote locations that not only make their
maintenance difficult, but also access to their measurements.
Typically the sensors are autonomous in the sense that they can run
for a certain time on battery power and store the measurement data in
internal memory. Only when the sensors are serviced, the measurement
data they have collected since the last servicing are uploaded to a
portable storage device. From there the data can be uploaded to
server. This manual procedure to retrieve sensor data is not only
error prone, but also results in a serious time lag between the time
the sensor performs the measurement and when it becomes available for
further processing. For many applications it would be beneficial to
have near-realtime access to the sensor measurement. Being able to
access data when they become available on the sensor device also
reduces the maintenance overhead.

>>>>

\author{\authorblockN{A. Puder, T. Johnson, K. Sales, M. de Sales}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: \{arno$\mid$tlj$\mid$klebers$\mid$msales\}@sfsu.edu}
\and
\authorblockN{D. Robinson}
\authorblockA{San Francisco State University \\
Romberg Tiburon Center \\
3150 Paradise Drive \\
Tiburon, CA 94920 \\
EMail: dhr@sfsu.edu}}

@@

Environmental monitoring depends on the reliable collection of
measurements from remotely deployed sensors and the rapid transfer of
those measurements to data centers where processing and analysis may
take place. Typically, sensors are deployed in out-of-the-way
locations, where physical access is limited and connections for
telemetry are poor or nonexistent. Maintaining the data stream from
these sensors places demands on human resources, requiring site visits
to service the sensors and to download data stored on internal memory.
Consequently, there is a lag of days to months between the time the
sensors perform the measurements and the time the measurements become
available. Advances in battery life and anti-fouling technology have
extended service cycles for field sensors, with the unwanted result of
further delaying access to monitoring data.  In addition, the
dependence on field site visits to alter of sensor characteristics, 
such as sampling rate, prevents adjustment in monitoring strategy in
response to rapidly developing events (e.g. oil spills, harmful algal
blooms).

To address these problems of data collection from remote
sensors, we propose to develop an automated end-to-end system based on
proven technology. It provides means to program and interrogate
sensors at the remote field locations and to transmit collected
measurements over long distances to data collections centers, where the
data is rapidly processed, archived, and made available to potential
users in near real-time.

@@

Researchers in the geosciences rely on sensor data collected by highly
specialized sensors such as the Seabird or YSI. These sensors are
usually deployed in remote locations that not only make their
maintenance difficult, but also access to their measurements.
Typically, the sensors are autonomous in the sense that they can run
for a certain time on battery power and store the measurement data in
internal memory. Only when the sensors are serviced, the measurement
data, which was collected since the last servicing, is uploaded to a 
portable storage device. From there, the data can be uploaded to
server. Notice that this manual procedure to retrieve sensor data is not only
error prone, but also results are in a serious time lag between the time
the sensor performs the measurement and when it becomes available for
further processing. For many applications, however, it would be beneficial to
have near-realtime access to the sensor measurement. In this way, being able 
to access data when they become available on the sensor device would also
reduce the maintenance overhead.
